{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-12-16 documents/brillouin_pulse_math.tex
Liposome test

@@

At a depth of 8 cm in Cole-Cole muscle, an 8 GHz resonance, attack pattern alpha appears to achieve 4 picometers of oscillation amplitude, rather than 0.01 picometers with $\sin(t\ \omega_{resonance})$.

@@

\begin{toolchain}
An arbitrary waveform propagates through a dispersive, lossy medium with a certain analytic dispersion relation. It then drives a
damped harmonic oscillator that is initially at rest.\\

@@

Quote Wait \cite{Propagation1965}:

\begin{quote}
	In such cases, it may be feasible to evaluate the integral by a purely numerical procedure. With the wide availability of the digital computer, this is certainly fashionable at the moment. Consequently, one might say that the problem has been solved and no further discussion is needed. \\

	However, it would be a pity if one accepted this answer since all physical insight into the nature of transient processes has been ignored. 
\end{quote}

@@

The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, This is based on a lagrange multiplier technique and variational calculus\footnotetext .

>>>>

Are similar to soliton

@@

At a depth of 8 cm in Cole-Cole muscle, an 8 GHz resonance, attack pattern alpha appears to achieve 4 picometers of oscillation amplitude, rather than 0.01 picometers with $\sin(t\ \omega_{resonance})$. The sharp edges are at approx. 250 GHz.

@@

\begin{toolchain}
An arbitrary waveform propagates through a dispersive, lossy medium with a certain analytic complex permittivity. It then drives a
damped harmonic oscillator that is initially at rest.\\

@@

\begin{fquote}[Wait][ \cite{Propagation1965}]
	In such cases, it may be feasible to evaluate the integral by a purely numerical procedure. With the wide availability of the digital computer, this is certainly fashionable at the moment. Consequently, one might say that the problem has been solved and no further discussion is needed. \\

	However, it would be a pity if one accepted this answer since all physical insight into the nature of transient processes has been ignored. 
\end{fquote}

@@

The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, This is based on a lagrange multiplier technique\cite{Methods1989} and variational calculus\footnotetext .
